Comparing Cross Validation Methods for Penalized Cox Regression

### 2018-02-27 cross-validation.tex
add new simulation figures and simulation code

   \begin{figure}[h]
   \centering
    \begin{minipage}[b]{0.4\textwidth}
      \centering
		  \includegraphics[height= 6cm ]{./figures/05.jpeg}
      \caption{ }
     \end{minipage}
     \begin{minipage}[b]{0.4\textwidth}
      \centering
		  \includegraphics[height= 6cm ]{./figures/06.jpeg}
      \caption{ }
      \end{minipage}	
   \end{figure}

@@

  \begin{table}[h]
    \centering
			\begin{tabular}{ c | c | c | c}
				CV Methods & $\lambda$ (SD) & MSE Ratio \\
				\hline \hline
				Optimal  & 0.0606 ( 0.0019 )&  / & \\ 
				Grouped  &  0.0895  ( 0.0043 )& 1.598  \\
				Ungrouped & 0.0754 ( 0.0060 )& 1.225 \\
				Linear Pred & 0.0759 ( 0.0058 )& 1.234 \\
				M Residual &0.1283 ( 0.0047 ) & 2.959
			\end{tabular}
			\caption{Simulation Results in High Dimensional Setting}
	\end{table}

>>>>

   \begin{figure}[h]
   \centering
    \begin{minipage}[b]{0.4\textwidth}
      \centering
		  \includegraphics[height= 6cm ]{./figures/05.png}
      \caption{ }
     \end{minipage}
     \begin{minipage}[b]{0.4\textwidth}
      \centering
		  \includegraphics[height= 6cm ]{./figures/06.png}
      \caption{ }
      \end{minipage}	
   \end{figure}

@@

 % \begin{table}[h]
   % \centering
%			\begin{tabular}{ c | c | c | c}
%				CV Methods & $\lambda$ (SD) & MSE Ratio \\
%				\hline \hline
%				Optimal  & 0.0606 ( 0.0019 )&  / & \\ 
%				Grouped  &  0.0895  ( 0.0043 )& 1.598  \\
%				Ungrouped & 0.0754 ( 0.0060 )& 1.225 \\
%				Linear Pred & 0.0759 ( 0.0058 )& 1.234 \\
%				M Residual &0.1283 ( 0.0047 ) & 2.959
%			\end{tabular}
%			\caption{Simulation Results in High Dimensional Setting}
%	\end{table}

\begin{table}[h]
\small
\centering
\caption{Simulation Results, Varying n and p}
\label{my-label}
\begin{tabular}{llllllllllllllll}
\hline
       & \multicolumn{3}{l}{n = 100, p = 20} &  & \multicolumn{3}{l}{n = 100, p = 100} &  & \multicolumn{3}{l}{n = 200, p = 1000} &  & \multicolumn{3}{l}{n = 500, p = 10000} \\
       & \multicolumn{3}{l}{$\#$of non-zero = 10} &  & \multicolumn{3}{l}{$\#$of non-zero = 10} &  & \multicolumn{3}{l}{$\#$of non-zero = 10} &  & \multicolumn{3}{l}{$\#$of non-zero = 20} \\ \cline{2-4} \cline{6-8} \cline{10-12} \cline{14-16} 
       &     &        &MSE       &  &   &       & MSE     &    &    &        & MSE      &  &     &        & MSE      \\
       & $\lambda$(SD)     & &Ratio       &  & $\lambda$(SD)         & & Ratio     & &$\lambda$(SD)         & & Ratio      & & $\lambda$(SD)         & & Ratio      \\ \cline{2-2} \cline{4-4} \cline{6-6} \cline{8-8} \cline{10-10} \cline{12-12} \cline{14-14} \cline{16-16} 
Optimal &           &        &          &  &           &       &          &  &           &        &          &  &           &        &          \\
Grouped &           &        &          &  &           &       &          &  &           &        &          &  &           &        &          \\
Ungrouped &           &        &          &  &           &       &          &  &           &        &          &  &           &        &          \\
Linear Pred &           &        &          &  &           &       &          &  &           &        &          &  &           &        &          \\
Deviance &           &        &          &  &           &       &          &  &           &        &          &  &           &        &          \\ \hline
\end{tabular}
\end{table}
